draft_final_assignment

### 2022-11-30 draft_final_assingment.Rmd
push rmd

---
title: "draft_final_assignment"
author: "Andrew Wells"
date: "11/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
library(plotly)
```

@@

##Creatung a dfm from the corpus
```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
  tokens_wordstem() %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program")) %>%
  dfm()

@@

##Most common words in the corpus
```{r }
dfmat %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```
#Wordcloud congress 115

```{r }
dfmat_115 <- dfm_subset(dfmat, session == 115)

@@

#Wordcloud congress 116

```{r }
dfmat_116 <- dfm_subset(dfmat, session == 116)

textplot_wordcloud(dfmat_116, max_words = 300)
```
#Wordcloud congress 117

```{r }
dfmat_117 <- dfm_subset(dfmat, session == 117)

@@

#Wordcloud comparing Democrats and Republicans
```{r }
dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
                     corp$party) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

#Wordcloud congress parties 115

```{r }

@@

#Wordcloud congress parties 116

```{r }

@@

#Wordcloud congress parties 117

```{r }

@@

#Wordcloud comparing Congresses
```{r }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

## Most common words (overall)
```{r}
#Overall most common words

@@

```{r}
#Republicans
dfmat_r <- dfm_subset(dfmat, party == "Republican")

@@

```{r}
#Democrats
dfmat_d <- dfm_subset(dfmat, party == "Democrat")

@@

```{r}
party_corp <- corpus_subset(corp, 
                            party %in% c("Democrat", "Republican"))

@@

```{r }
# Most common words by Congressional session 115
tfreq_115 <- dfmat_115 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r }
# Most common words by Congressional session 116
tfreq_116 <- dfmat_116 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r}
# Most common words by Congressional session 117
tfreq_117 <- dfmat_117 %>%
  textstat_frequency() %>%
  head(20)

@@

##Comparing subgroups
```{r}
df <- df %>%
  mutate(session_written = ifelse(session == 115, "session_115", 
                             ifelse(session == 116, "session_116",
                             ifelse(session == 117, "session_117", NA))))

@@

```{r}
sims <- textstat_simil(dfmat, method="cosine")

sim_df <- as.data.frame(sims, upper = TRUE)

sim_df
```

##Dimensionality plotting

@@

##Topic modeling

@@

##Sentiments

@@

ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party_full)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
##Some machine learning

>>>>

---
title: "draft_final_assignment"
author: "Andrew Wells"
date: "11/18/2022"
output: 
  html_document:
    toc: TRUE
    theme: cosmo
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
library(plotly)
```

@@

## Creatung a dfm from the corpus
```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
  tokens_wordstem() %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program","requir","divis","titl","appropri","specifi")) %>%
  dfm()

@@

## Most common words in the corpus
```{r }
dfmat %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```

# Wordclouds

## Wordcloud congress 115

```{r, wa }
dfmat_115 <- dfm_subset(dfmat, session == 115)

@@

## Wordcloud congress 116

```{r, wa }
dfmat_116 <- dfm_subset(dfmat, session == 116)

textplot_wordcloud(dfmat_116, max_words = 300)
```
## Wordcloud congress 117

```{r, wa }
dfmat_117 <- dfm_subset(dfmat, session == 117)

@@

## Wordcloud comparing Democrats and Republicans
```{r, wa }
dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
                     corp$party) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

## Wordcloud congress parties 115

```{r, wa }

@@

## Wordcloud congress parties 116

```{r, wa }

@@

## Wordcloud congress parties 117

```{r, wa }

@@

## Wordcloud comparing Congresses
```{r, wa }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

## Most common words (overall)
```{r, warning=FALSE}
#Overall most common words

@@

```{r, warning=FALSE}
#Republicans
dfmat_r <- dfm_subset(dfmat, party == "Republican")

@@

```{r, warning=FALSE}
#Democrats
dfmat_d <- dfm_subset(dfmat, party == "Democrat")

@@

```{r, warning=FALSE}
party_corp <- corpus_subset(corp, 
                            party %in% c("Democrat", "Republican"))

@@

```{r, warning=FALSE}
# Most common words by Congressional session 115
tfreq_115 <- dfmat_115 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r, warning=FALSE}
# Most common words by Congressional session 116
tfreq_116 <- dfmat_116 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r, warning=FALSE}
# Most common words by Congressional session 117
tfreq_117 <- dfmat_117 %>%
  textstat_frequency() %>%
  head(20)

@@

## Comparing subgroups
```{r, warning=FALSE}
df <- df %>%
  mutate(session_written = ifelse(session == 115, "session_115", 
                             ifelse(session == 116, "session_116",
                             ifelse(session == 117, "session_117", NA))))

@@

```{r}
# sims <- textstat_simil(dfmat, method="cosine")
# 
# sim_df <- as.data.frame(sims, upper = TRUE)
# 
# sim_df
```

## Dimensionality plotting

@@

## Topic modeling

@@

## Sentiments

@@

ggplot(daily_sentiment_117, aes(x=date, y = score, colour=party_full)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + 
  theme_minimal() + 
  geom_smooth(method = "lm")
```
## Some machine learning
